\documentclass[sigconf]{acmart}
% * <erishabh@gmail.com> 2017-06-26T11:25:04.108Z:
%
% ^.

\usepackage{booktabs} % For formal tables
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{color}
\usepackage{caption}
\usepackage{hyperref}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
  Paso, Texas USA} 
\acmYear{1997}
\copyrightyear{2016}

\acmPrice{15.00}


\begin{document}
\title{Exploiting Structured Elements to improve Retrieval}
\titlenote{Work in progress.}
  
  \author{Manisha Verma}
\affiliation{
  %\institution{Dept of Computer Science}
  \streetaddress{University College London}
  %\city{London} 
  %\state{United Kingdom} 
}
\email{m.verma@cs.ucl.ac.uk}


\author{Rishabh Mehrotra}
\affiliation{
  %\institution{Dept of Computer Science}
  \streetaddress{University College London}
  %\city{London} 
  %\state{United Kingdom} 
}
\email{r.mehrotra@cs.ucl.ac.uk}

\author{Emine Yilmaz}
\affiliation{
       \streetaddress{University College London}     
}
  \email{emine.yilmaz@ucl.ac.uk}
\begin{abstract}
Word embeddings have recently been shown to be effective in improving retrieval. 
However, existing word embeddings rely on plain text and do not take into consideration the 
structure of a web document which is traditionally a popular means of extracting 
features for query-document matching. The underlying assumption of existing word embeddings 
from plain text documents is that semantically related words occur together. However, 
these embeddings may not provide a succinct representation of web documents. Webpages provide  
a lot more meta-information about each word. We can extract multiple properties of a word such 
as its color, size or location in a webpage. Integration of these properties into existing word 
embeddings would yield a much richer representation of web documents which can be used to perform 
several tasks such as clustering, retrieval or spam detection. 

In this preliminary work, we exploit these structural properties to create 
richer embeddings for web documents. We specifically exploit location of words and structure 
of web page to create these embeddings. We evaluate the utility of these embeddings with retrieval. 
Our experiments show that structure embeddings clearly outperform plain text word embeddings 
on four years of Web track TREC corpus. 

\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
% \begin{CCSXML}
% <ccs2012>
%  <concept>
%   <concept_id>10010520.10010553.10010562</concept_id>
%   <concept_desc>Computer systems organization~Embedded systems</concept_desc>
%   <concept_significance>500</concept_significance>
%  </concept>
%  <concept>
%   <concept_id>10010520.10010575.10010755</concept_id>
%   <concept_desc>Computer systems organization~Redundancy</concept_desc>
%   <concept_significance>300</concept_significance>
%  </concept>
%  <concept>
%   <concept_id>10010520.10010553.10010554</concept_id>
%   <concept_desc>Computer systems organization~Robotics</concept_desc>
%   <concept_significance>100</concept_significance>
%  </concept>



%  <concept>
%   <concept_id>10003033.10003083.10003095</concept_id>
%   <concept_desc>Networks~Network reliability</concept_desc>
%   <concept_sigificance>100</concept_significance>
%  </concept>
% </ccs2012>  
% \end{CCSXML}
% 
% \ccsdesc[500]{Computer systems organization~Embedded systems}
% \ccsdesc[300]{Computer systems organization~Redundancy}
% \ccsdesc{Computer systems organization~Robotics}
% \ccsdesc[100]{Networks~Network reliability}

% We no longer use \terms command
%\terms{Theory}

\keywords{document representations; structural elements; word embeddings; retrieval}


\maketitle
\input{introduction}
\input{related_work}
\input{methodology}
\input{results}
\input{conclusion}


%\bibliographystyle{ACM-Reference-Format}
\bibliographystyle{plain}
\bibliography{sample-sigconf} 

\end{document}
